INTELLIGENT SYSTEMS

### 2021-03-29 slides.tex
finish applications paper2 slide

\documentclass[10pt]{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{biblatex}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{caption}[numbered]
\bibliography{Bibliography}

@@

\begin{frame}{LSC Algorithm pt2}
    Assuming that equation 1 exists, LSC method takes two parameters as 
    input; The image to be segmented and the preferred K number of 
    superpixels that the algorithm will have to produce.
\end{frame}

>>>>

\documentclass[10pt]{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{biblatex}
\usepackage{adjustbox}
\usepackage[font=scriptsize]{caption}
\usepackage{subcaption}
\captionsetup[figure]{labelsep=period}
\captionsetup[subfigure]{labelformat=simple} % default is 'parens'
\renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}

\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{caption}[numbered]
\bibliography{Bibliography}

@@

\begin{frame}{LSC Algorithm pt2}
    Assuming that equation 1 exists, LSC method takes two parameters as 
    input; The image to be segmented and the preferred K number of 
    superpixels that the algorithm will have to produce. The number K 
    corresponds to the number of centroids and each of these will be useful 
    for grouping the neighbors pixels, in a range of $ \tau v_x \ x \ \tau v_y $, with $ \tau>0.5 $, 
    using a distance comparison.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.7 \linewidth]{paper2/slide1.png}
        \centering
        \caption{Sample images segmented with K = 1000/500/200 superpixels using LSC.}
        \label{fig: metrics}
    \end{figure}
\end{frame}

\begin{frame}{COMPARATIVE EXPERIMENTS}
    \begin{table}[htbp!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{*{9}{|c}|}%%{|c|c|c|c|c|c|c|c|c|}
            \hline
            & EneOpt0 & SEEDS\footfullcite{0781426509} & ERS\footfullcite{0781426508} & Lattices & NCuts & SLIC\footfullcite{0781426514} & Turbo & LSC \\
            \hline
            \bfseries{ADERENCE TO BOUNDARY} & & & & & & & & \\
            \emph{Under segmentation error} & 0.230 & 0.197 & 0.198 & 0.303 & 0.220 & 0.213 & 0.277 & \bfseries{0.190}\\
            \emph{Boundary recall} & 0.765 & 0.918 & 0.920 & 0.811 & 0.789 & 0.837 & 0.739 & \bfseries{0.926}\\
            \emph{Achievable segmentation accuracy} & 0.950 & 0.960 & 0.959 & 0.933 & 0.956 & 0.956 & 0.943 & \bfseries{0.962}\\
            \hline
            \bfseries{SEGMENTATION SPEED} & & & & & & & & \\
            \emph{Computational complexity} & $ O(N^3/K^2) $ & $ O(N) $ & $ O(N^2 \lg{N}) $ & $ O(N^{\frac{3}{2}} \lg{N}) $ & $ O(N^{\frac{3}{2}}) $ & $ O(N) $ & $ O(N) $ & $ O(N) $\\
            \emph{Average time per image} & 3.35s & \bfseries{0.0935}s & 0.969s & 0.284s & 93.4s & 0.125s & 6.61s & 0.334s\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Performance metrics superpixel segmentation algorithms at K=400}
        \label{table superpixels}
    \end{table}
    Best performance: low "Under segmentation Error" (\emph{UE}), high 
    "Boundary Recall" (\emph{BR}) and high "Achievable segmentation accuracy 
    (\emph{ASA}).
\end{frame}

\begin{frame}{APPLICATIONS: Class segmentation}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper2/superpixelAlgo.png}
        \centering
        \caption{Segmentation using different superpixels algorithms. (a) Original Image. (b) QS. (c) ERS. (d) SLIC. (e) LSC. (f)Ground Truth.}
        \label{fig: superpixelSegmentation}
    \end{figure}

    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=4cm}
        \begin{tabular}{*{5}{|c}|}%%{|c|c|c|c|c|}
            \hline
            & QS & ERS & SLIC & LSC\\
            \hline
            bike & 72.2 & 74.2 & 76.3 & \bfseries{76.9}\\
            cars & 72.2 & 74.7 & 72.5 & \bfseries{76.8}\\
            person & 66.3 & 66.5 & 66.7 & \bfseries{67.0}\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy using different superpixels algorithms.}
        \label{table accuracy}
    \end{table}
\end{frame}

\begin{frame}{APPLICATIONS: Weakly Supervised Semantic Segmentation}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width = 0.7 \linewidth]{images/paper2/semanticSegmentation.png}
                \caption{Weakly supervised semantic segmentation. (a) A training image with bounding boxes. (b) Output of soft-max layer of $ FCN_c $. (c) Coarse semantic segmentation result. (d) Superpixels with higher probability of foreground. (e) Fore-/Background segmentation result after iterative optimization. (f) Refined semantic segmentation result.}
            \end{figure}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper2/segmentationAlgo.png}
                \centering
                \caption{Semantic segmentation. (a) Input image. (b) Strong. (c) Bbox-seg. (d) $ Joint_{sp} $ (LSC) }
            \end{figure}
            \begin{table}[H]
                \begin{adjustbox}{max width=4cm}
                    \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
                        \hline
                        Strong\footnotemark[1]& Bbox-seg\footnotemark[1] & $ Joint_{sp} $ \\
                        \hline
                        62.5 & 60.6 & \bfseries{64.0} \\
                        \hline
                    \end{tabular}
                \end{adjustbox}
                \caption{Semantic segmentation accuracy in terms of Mean IOU (\%)}
            \end{table}
        \end{minipage}
    \end{minipage}
    \footnotetext[1]{\tiny G. Papandreou, L. Chen, K. Murphy, and A. Yuille, “Weakly-and semi-
    supervised learning of a deep convolutional network for semantic image
    segmentation,” in Proc. ICCV, pp. 1742–1750, Dec. 2015}
